---
title: "Genetic Association Analysis with R (II)"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
fontsize: 11pt
bibliography: '`r system.file("REFERENCES.bib", package="gaawr2")`'
csl: nature-genetics.csl
pkgdown:
  as_is: true
vignette: >
  %\VignetteIndexEntry{gaawr2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
set.seed(0)
knitr::opts_chunk$set(
  out.extra = 'style="display:block; margin: auto"',
  fig.align = "center",
  fig.path = "gaawr2/",
  collapse = TRUE,
  comment = "#>",
  dev = "png")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pkgs <- c("knitr")
for (p in pkgs) if (length(grep(paste("^package:", p, "$", sep=""), search())) == 0) {
    if (!requireNamespace(p)) warning(paste0("This vignette needs package `", p, "'; please install"))
}
invisible(suppressMessages(lapply(pkgs, require, character.only = TRUE)))
```

This package intends to gather information, meta-data and relevant scripts in genetic association analysis as a companion to a Henry-Stewart talk.

The package is adapted from earlier package development work,  particularly pQTLdata.

# Setup

The relevant scripts are with `inst/scripts` directory in the source package. Briefly,

- `create_github_pository.sh` is called to create `gaawr2` at GitHub from the command line.
- `create_package.R` is used to create the package in R.
- `pkgdown.sh` is called to make a pkgdown-style package and this vignette is set to be processed with the `bookdown` package.
- `docs.sh` is used to push files to GitHub.

Note that for creation of the GitHub repository, a SSH key is already in place.

A GitHub login is still necessary to enable web pages, so that this can be accessed as <https://jinghuazhao.github.io/gaawr2/>.

Upon use `pkgdown`, an article can be seen as <https://jinghuazhao.github.io/gaawr2/articles/index.html>.

We carry on adding files such as `NEWS.md` and `pkgdown.yml`.

# Mode of execution
