---
title: "Web facilities"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: true
fontsize: 11pt
bibliography: '`r system.file("REFERENCES.bib", package="gaawr2")`'
csl: nature-genetics.csl
pkgdown:
  as_is: true
vignette: >
  %\VignetteIndexEntry{Web facilities}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
set.seed(0)
knitr::opts_chunk$set(
  out.extra = 'style="display:block; margin: auto"',
  fig.align = "center",
  fig.path = "plumber/",
  collapse = TRUE,
  comment = "#>",
  dev = "png")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pkgs <- c("httr","httpuv","jsonlite","plumber","seqminer")
for (p in pkgs) if (length(grep(paste("^package:", p, "$", sep=""), search())) == 0) {
    if (!requireNamespace(p)) warning(paste0("This vignette needs package `", p, "'; please install"))
}
invisible(suppressMessages(lapply(pkgs, require, character.only = TRUE)))
```

Perhaps this is the simplest way to start from the Linux command line, nevertheless with Python,

```python
python3 -m http.server 8000
firefox http://127.0.0.1:8000
```

which works even with `python3 -m http.server` when the port number 8000 is available.

However we leave this as a benchmark, and our focus here is R with the following script,

```r
httpuv::startServer("0.0.0.0", 8000, list(
  call = function(req) {
    list(
      status = 200L,
      headers = list("Content-Type" = "text/plain"),
      body = "Hello, world!"
    )
  })
)
```

upon access http://127.0.0.1:8000, we see the message "Hello, world!". 

Below, we assume that our working directory is either

- `inst/` in the **gaawr2** source package.
- the directory for the installed package.

# plumber

It is `an API generator in R`, which has been tested through Caprion data as follows.

As noted elsewhere, `libsodium` is required for installation of the R package.

```r
get_data <- function(filename, region)
{
  query_result <- seqminer::tabix.read(filename, region)
  hdr <- c("Chromosome", "Position",
           "MarkerName", "Allele1", "Allele2", "Freq1", "FreqSE", "MinFreq", "MaxFreq",
           "Effect", "StdErr", "logP",
           "Direction", "HetISq", "HetChiSq", "HetDf", "logHetP", "N")
  df <- read.table(text = paste(query_result, collapse = "\n"), sep = "\t", col.names=hdr)
  return(df)
}

plbr <- plumber::Plumber$new()
plbr$handle("GET", "/tests", function(req, res) {
  protein <- req$args$protein
  region <- req$args$region
  if (is.null(protein) || is.null(region)) {
    res$status <- 400
    return(list(error = "Both 'protein' and 'region' must be provided"))
  }
  filename <- file.path("tests",paste0(protein,"-1.tbl.gz"))
  print(filename)
  if (!file.exists(filename)) {
    res$status <- 404
    return(list(error = paste("File for", protein, "not found")))
  }
  data <- get_data(filename, region)
  json_data <- toJSON(data, dataframe = "rows", na = "null")
  res$setHeader("Content-Type", "application/json")
  return(json_data)
})
plbr$run(port = 8001)
```

We can see that,

```
> options(width = 200)
> filename <- file.path("tests","IL.18R1-1.tbl.gz")
> region <- "2:102700000-103800000"
> data <- get_data(filename, region)
> head(data,1)
  Chromosome  Position         MarkerName Allele1 Allele2 Freq1 FreqSE MinFreq MaxFreq  Effect StdErr  logP   Direction HetISq HetChiSq HetDf logHetP     N
1          2 102700138 chr2:102700138_A_G       a       g 0.087 0.0207  0.0641  0.1376 -0.0566 0.0239 -1.75 -?-+n-?--n+   78.2   36.757     8  -4.894 12799
```

and

```
Running plumber API at http://127.0.0.1:8001
Running swagger Docs at http://127.0.0.1:8001/__docs__/
```

So we get query results in JSON format from

- **browser**: http://localhost:8001/tests?protein=IL.18R1&region=2:102700000-103800000
- **curl**: curl "http://localhost:8001/tests?protein=IL.18R1&region=2:102700000-103800000"

Additional work required to get output from `curl` to a tab-delimited data,

```bash
curl "http://localhost:8001/tests?protein=IL.18R1&region=2:102700000-103800000" | \
jq -r '.[0] |
   fromjson |
   .[] |
   [
     .Chromosome, .Position, .MarkerName, .Allele1, .Allele2, .Freq1,
     .Effect, .StdErr, .logP, .Direction, .HetISq, .HetChiSq, .HetDf, .logHetP, .N
   ] |
   @tsv'
```

where

1. **.[0]**: Access the first element in the outer array (the string containing the JSON).
2. **fromjson**: Parse the string into a JSON object.
3. **.[]**: Iterate over the array inside the parsed JSON.
4. **[ ... ]**: Create an array of the values needed, each corresponds to a column in the TSV output.
5. **@tsv**: Convert the array into tab-separated values.

Note also that only selected columns (as in 4) are kept. The simplest way to have the header is add it manually,

```bash
(
  echo "Chromosome|Position|MarkerName|Allele1|Allele2|Freq1|Effect|StdErr|logP|Direction|HetISq|HetChiSq|HetDf|logHetP|N" | \
  sed 's/|/\t/g'
  curl command as above.
)
```

# httpuv

A somewhat more involved version is as follows,

```r
dir.create("content/assets", recursive = TRUE)
dir.create("content/lib", recursive = TRUE)
s <- httpuv::startServer(
  host = "0.0.0.0", 
  port = 5000,
  app = list(
    call = function(req) {
      list(
        status = 200L,
        headers = list(
          'Content-Type' = 'text/html',
          'Access-Control-Allow-Origin' = '*',
          'Access-Control-Allow-Methods' = 'GET, POST, OPTIONS',
          'Access-Control-Allow-Headers' = 'Content-Type'
        ),
        body = "Hello world!"
      )
    },
    staticPaths = list(
      "/assets" = "content/assets/", # Static assets
      "/lib" = httpuv::staticPath("content/lib", indexhtml = FALSE),
      "/lib/dynamic" = httpuv::excludeStaticPath()
    ),
    staticPathOptions = httpuv::staticPathOptions(indexhtml = TRUE)
  )
)
cat("Server running at http://0.0.0.0:5000\n")
s$stop()
```

# References
